A demonstration of the \LaTeXe\ class file for \itshape{\journalnamelc}\footnotemark[2]

### 2019-01-26 journal/conclusions.tex
right format

\section{Conclusions and Future Work}
\label{conc}
\comment{
When are two failing test cases due to the same fault?  This paper
demonstrates that
``when they are repaired by the same program mutants'' is a useful answer to
this question.  The problem of causality in executions is hard, and
has long been tied to a notion of similarity of
executions \cite{NearNeighbor,GroceError}. } By using program changes
(produced by mutants) as
causes to determine distance, it is possible to improve on efforts
to identify the set of faults in a large set of redundant compiler failures
\cite{PLDI13} and discover the source code locations of faults
\cite{MUSE,multilingual}.  For a set of more than 2,800 tests and more
than 50 faults, over the Mozilla SpiderMonkey 1.6 JavaScript compiler and
GCC 4.3.0, our methods improve fault identification (``fuzzer taming''), in a statistically significant way
(with effect size of about 3\% improvement), over
the \emph{best} (for each subject program) of over 16 metrics considered in previous work.
Preliminary investigation also shows improvement (for a shared
mutation testing budget) over previous mutant-based fault localization
methods, for the same tests and a subset of 24 faults with known
locations.  Our {\bf Repair} method, in particular, was the only
localization approach to provide any perfect localizations of faults
(it produced 3),
and provided three times as many very-high-quality (ranking the fault
in top 5 locations) localizations as the next best method
\cite{multilingual}  --- 6 such localizations, compared to only 2.
For GCC wrong-code faults, only our methods produced any
very-high-quality fault localizations.  When applied to non-compiler
faults, the metric tended to either not produce a localization,
produce a very small incorrect localization (1-3 statements), or
produce a very high quality localization.  Restricting to the cases
where we consider {\bf Repair} applicable (7 faults) {\bf Repair}
perfectly localized 4 of them, and produced a 1 or 2 statement
incorrect localization for the others.

As future work, we plan to apply the mutation-based metric to other
fuzzer taming and fault localization problems.  The highly varying
results for even the best fault localization methods in our
experiments demonstrate that further advances are required before
compiler debugging can consistently be made less onerous through automated
assistance.  \comment{One idea is to combine the metric approach and fall
the ideas
in MUSE and MUSEUM, or other mutant-based localizations such as
Metallaxis \cite{Metallaxis} in some way, to exploit passing tests and perhaps
additional coverage information.  We would also be very interested to
compare our localizations with the Metallaxis
\cite{Metallaxis,Papadakis} approach.}

>>>>

\section{Conclusions and Future Work}
\label{conc}
When are two failing test cases due to the same fault?  This paper
demonstrates that
``when they are repaired by the same program mutants'' is a useful answer to
this question.  The problem of causality in executions is hard, and
has long been tied to a notion of similarity of
executions \cite{NearNeighbor,GroceError}.  By using program changes
(produced by mutants) as
causes to determine distance, it is possible to improve on efforts
to identify the set of faults in a large set of redundant compiler failures
\cite{PLDI13} and discover the source code locations of faults
\cite{MUSE,multilingual}.  For a set of more than 2,800 tests and more
than 50 faults, over the Mozilla SpiderMonkey 1.6 JavaScript compiler and
GCC 4.3.0, our methods improve fault identification (``fuzzer taming''), in a statistically significant way
(with effect size of about 3\% improvement), over
the \emph{best} (for each subject program) of over 16 metrics considered in previous work.
Preliminary investigation also shows improvement (for a shared
mutation testing budget) over previous mutant-based fault localization
methods, for the same tests and a subset of 24 faults with known
locations.  Our {\bf Repair} method, in particular, was the only
localization approach to provide any perfect localizations of faults
(it produced 3),
and provided three times as many very-high-quality (ranking the fault
in top 5 locations) localizations as the next best method
\cite{multilingual}  --- 6 such localizations, compared to only 2.
For GCC wrong-code faults, only our methods produced any
very-high-quality fault localizations.  When applied to non-compiler
faults, the metric tended to either not produce a localization,
produce a very small incorrect localization (1-3 statements), or
produce a very high quality localization.  Restricting to the cases
where we consider {\bf Repair} applicable (7 faults) {\bf Repair}
perfectly localized 4 of them, and produced a 1 or 2 statement
incorrect localization for the others.

As future work, we plan to apply the mutation-based metric to other
fuzzer taming and fault localization problems.  The highly varying
results for even the best fault localization methods in our
experiments demonstrate that further advances are required before
compiler debugging can consistently be made less onerous through automated
assistance.

### 2019-01-26 journal/experiments.tex
right format

\comment{
We applied our metric to two of the datasets used in the previous study of compiler fuzzer taming \cite{PLDI13}: faults and tests cases for SpiderMonkey 1.6, Mozilla's JavaScript engine, with tests generated by {\tt jsfunfuzz} \cite{jsfunfuzz}, and \emph{wrong code} faults and test cases for GCC 4.3.0, with tests generated by Csmith \cite{csmith}.   We did not use the crash faults from that data set, as these are in practice fairly easy to identify by hand (and perfectly identified by previous metrics), and also typically easy to debug.  }

@@

Table \ref{bothtable} shows a comparison of three fault localization methods for the SpiderMonkey (and GCC) faults.  The first column is a fault ID. The next three columns show localization rankings.  A dash for a column means that localization did not rank any faulty statements, or assigned all faulty statements suspiciousness of 0.0.  The three rankings are: our {\bf Repair} localization, the MUSE \cite{MUSE} localization, and the MUSEUM \cite{multilingual} localization.  MUSEUM uses the same formula as MUSE, but works better for multiple faults because it uses only one failure.  The MUSE/MUSEUM formulas normally make use of information from passing tests as well: when mutating a statement makes a passing test case fail, it makes the statement \emph{less} suspicious, by a weighted amount. The weight assigned to information from passing tests in our setting would likely be low (due to the ratios of repairs to mutation kills).  In a limited sense, information from passing tests is already incorporated in our results.  Throwing out all mutants that are killed by any passing test as potential repairs/localizations ensures that the rankings of all statements that are in MUSE/MUSEUM rankings are correct, \emph{relative to each other}.  By definition, passing tests have no influence on the suspiciousness of these mutants.  However, there may be other mutants that 1) repair a failure and 2) are killed by some test case: these could, if enough different ones repaired the same faulty statement, improve MUSE/MUSEUM results, though in practice this is extremely unlikely.  We reject such mutants in part to keep costs low, and in part because we think that the causal information contained in such mutants, that ``fix'' a failure but also break some passing test(s), is problematic.  They seem likely to be less useful as explanations of the causes of a failure, since they do not impact the program semantics in a way that is only known to be beneficial, and could potentially even mislead a user if used as explanations.  \comment{Still, it is most useful to compare MUSEUM/MUSE and our approach on the cases where all methods produce a localization.}

@@

\comment{
\begin{table}
\centering
{\scriptsize
\begin{tabular}{|c||c|c|c|}
\hline
%& \multicolumn{3}{|c|}{Localization Rank} \\
%\hline
Fault & Repair & MUSE & MUSEUM \\
\hline
880 & - & - & - \\
95 & - & 173 & -\\
1294 & 1 & 22 & 4 \\
60 & - & - & -\\
1543 & 19 & 118 & 26\\
1172 & 28 & 87 & 23\\
1561 & - & - & - \\
115 & 3 & 133 & 5 \\
\hline
\end{tabular}
}
\caption{Fault localization results for SpiderMonkey}
%\vspace{-0.2in}
\label{jstable}
\end{table}
}

@@

\comment{
\begin{table}
\centering
{\scriptsize
\begin{tabular}{|c||c||c|c|}
\hline
%& & \multicolumn{4}{|c|}{Localization Rank} \\
%\hline
Fault & Repair & MUSE & MUSEUM \\
\hline
139094 & - & 157 & -\\
133004 & 1 & 99 & 14\\
158782 & - & 146 & -\\
156496 &  - & - & -\\
143677 & - & 109 & -\\
158555 & - & - & -\\
134321 & - & - & -\\
133940 & 4 & 158 & 18\\
141195 & - & - & -\\
156795 & - & - & -\\
139709 & 10 & 167 & 6\\
155698 & 1 & 172 & 195\\
138646 & - & - & -\\
140795 & 34 & 170 & 125\\
136501 &  5 & 159 & 31\\
134322 & - & - & -\\
\hline
\end{tabular}
}
\caption{Fault localization results for GCC}
\label{gcctable}
\end{table}
}

@@

%\comment{
 Why does {\bf Repair} perform best in the \emph{compiler} setting in particular?  It is impossible to be sure, but one  possibility is power to distinguish repairs.  If there are many repairs for a failure, how can the most important ones be distinguished?  MUSEUM relies on a large set of mutation operators, and assumes that faulty statements will have multiple repairs, compared to non-faulty statements, or that faulty statements will be less likely to cause passing tests to fail when mutated.  Restricting ourselves to cases where {\bf Repair} and MUSEUM both provided a localization, we know that some faulty statement was in a repairing mutant, but that passing tests could not distinguish this mutant  from other repairs (since we only use repairs that cause no passing tests to fail).  Many of the faulty statement repairs (as expected for optimizing compilers) were statement deletions and conditional negations.  For these, it seems unlikely that Proteum would produce more mutants repairing the statement, though perhaps Proteum would create repairs for other statements that cannot be modified into a repair by any of Andrews' operators.  Our suspicion is somewhat confirmed by the results below where we used our methods with the MUSEUM mutant result set.

@@

\comment{ For the compiler faults, if any repair for a failure modified a faulty statement, {\bf Repair} always ranked it in the top 34 localizations, ranked it in the top 5 in 6 of 10 such cases, and 3 times ranked it 1st.  MUSEUM, in contrast, ranked one such repair 195th, never ranked a fault in its top 3 statements, and only ranked a fault in its top 5 statements twice.  Of course, MUSEUM might be suffering from a lack of mutation operators, but in some cases this is unlikely due to the nature of the repairs.  }

\comment{ In one sense, {\bf Coverage} is the most intriguing method presented here.  While it did not perform nearly as well as {\bf Repair}, it did manage, in many cases, to rank \emph{some} faulty line highly relative to the extremely large number of statements executed in each failing GCC run (on the order of 50K-100K+ statements).  In future work, we plan to experiment with different methods for weighting frequency of coverage, perhaps using methods from machine learning, or of pruning changed coverage that is not likely to be relevant.  For example, perhaps the {\bf Repair} approach can be applied, and coverage changes present in very distant failures can be removed, though the argument is less clear, since a coverage change isn't directly associated with the onion-ring structure, and does not directly repair a set of failures.  There is much to be done if automated debugging is ever to make the lives of compiler developers easier in most cases \cite{AutoHelp}.  }

>>>>

@@

Table \ref{bothtable} shows a comparison of three fault localization methods for the SpiderMonkey (and GCC) faults.  The first column is a fault ID. The next three columns show localization rankings.  A dash for a column means that localization did not rank any faulty statements, or assigned all faulty statements suspiciousness of 0.0.  The three rankings are: our {\bf Repair} localization, the MUSE \cite{MUSE} localization, and the MUSEUM \cite{multilingual} localization.  MUSEUM uses the same formula as MUSE, but works better for multiple faults because it uses only one failure.  The MUSE/MUSEUM formulas normally make use of information from passing tests as well: when mutating a statement makes a passing test case fail, it makes the statement \emph{less} suspicious, by a weighted amount. The weight assigned to information from passing tests in our setting would likely be low (due to the ratios of repairs to mutation kills).  In a limited sense, information from passing tests is already incorporated in our results.  Throwing out all mutants that are killed by any passing test as potential repairs/localizations ensures that the rankings of all statements that are in MUSE/MUSEUM rankings are correct, \emph{relative to each other}.  By definition, passing tests have no influence on the suspiciousness of these mutants.  However, there may be other mutants that 1) repair a failure and 2) are killed by some test case: these could, if enough different ones repaired the same faulty statement, improve MUSE/MUSEUM results, though in practice this is extremely unlikely.  We reject such mutants in part to keep costs low, and in part because we think that the causal information contained in such mutants, that ``fix'' a failure but also break some passing test(s), is problematic.  They seem likely to be less useful as explanations of the causes of a failure, since they do not impact the program semantics in a way that is only known to be beneficial, and could potentially even mislead a user if used as explanations.

@@

@@

@@

 Why does {\bf Repair} perform best in the \emph{compiler} setting in particular?  It is impossible to be sure, but one  possibility is power to distinguish repairs.  If there are many repairs for a failure, how can the most important ones be distinguished?  MUSEUM relies on a large set of mutation operators, and assumes that faulty statements will have multiple repairs, compared to non-faulty statements, or that faulty statements will be less likely to cause passing tests to fail when mutated.  Restricting ourselves to cases where {\bf Repair} and MUSEUM both provided a localization, we know that some faulty statement was in a repairing mutant, but that passing tests could not distinguish this mutant  from other repairs (since we only use repairs that cause no passing tests to fail).  Many of the faulty statement repairs (as expected for optimizing compilers) were statement deletions and conditional negations.  For these, it seems unlikely that Proteum would produce more mutants repairing the statement, though perhaps Proteum would create repairs for other statements that cannot be modified into a repair by any of Andrews' operators.  Our suspicion is somewhat confirmed by the results below where we used our methods with the MUSEUM mutant result set.

@@

### 2019-01-26 journal/localizations.tex
right format

Automated fault localization \cite{FaultSurvey,Jones2002} provides users with
information about the likely location of a fault in a program's source
code.  \comment{Error explanation \cite{GroceError} also provides information
about the causal structure of a fault --- how it can be avoided, what
triggers it --- a kind of ``fault story.''}  Parnin and Orso recently
suggested that fault localization methods are not actually providing a
great deal of assistance to real users in debugging \cite{AutoHelp}.
Automated fault localization has not been widely adopted in industry.

>>>>

Automated fault localization \cite{FaultSurvey,Jones2002} provides users with
information about the likely location of a fault in a program's source
code.  Error explanation \cite{GroceError} also provides information
about the causal structure of a fault --- how it can be avoided, what
triggers it --- a kind of ``fault story.''  Parnin and Orso recently
suggested that fault localization methods are not actually providing a
great deal of assistance to real users in debugging \cite{AutoHelp}.
Automated fault localization has not been widely adopted in industry.

### 2019-01-26 journal/metrics.tex
right format

This metric, the portion of mismatches over bits that are 1 in either
vector, matches our intuitions about the above comparisons.  It
essentially formalizes the intuition of the onion-ring model, where
more matching repairs indicates a much higher probability two failures
are due to the same fault, even if not all repairs match.
\comment{
\footnote{In Section \ref{conc} we discuss uses of $d$
requiring comparison of both failing and passing test cases:  in this 
case, we would use three-valued vectors, where 1 indicates a 
failing property succeeds and -1 that a succeeding property 
fails.  For such an application, we could remove the requirement that
a repair not be a killed mutant, since the passing test vectors would encode
that information.}}

>>>>

This metric, the portion of mismatches over bits that are 1 in either
vector, matches our intuitions about the above comparisons.  It
essentially formalizes the intuition of the onion-ring model, where
more matching repairs indicates a much higher probability two failures
are due to the same fault, even if not all repairs match.
